IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-10-17 paper/appendix.tex
move semantics to appendix

>>>>

\section{Full Semantics for |targetLangML|}
\label{sec:app:semantics}

In Figure~\ref{fig:ml-full} we give the full semantics for |targetLangML|.  A subset
of them has been given in Figure~\ref{fig:ml} earlier in the paper.

\begin{figure}
\begin{code}
tv   ::= \tx.te | true | false | ta
te   ::= tv | tx | te te | if te then te else te | ref te | !te | te := te | fix te
tE   ::= tHole | tE te | tv tE | if tE then te else te | ref tE | !tE | tE := te | tv := tE | fix tE
te1 ; te2            @= (\tx.te2) te1  where  tx notmember FV(te2)
let tx = te1 in te2  @= (\tx.te2) te1
\end{code}
\begin{mathpar}

\inferrule[T-app]
{ } {| conf tS ((\x.te) tv) -> conf tS ({tv/x} te) |}

\and
\inferrule[T-ifTrue]
{ } {| conf tS (if true then te1 else te2) -> conf tS te1|}

\and
\inferrule[T-ifFalse]
{ } {| conf tS (if false then te1 else te2) -> conf tS te2|}

\and
\inferrule[T-ref]
{ | fresh ta | }
{| conf tS (ref tv) -> conf (bracket tS (mapsto ta tv)) ta |}

\and
\inferrule[T-deref]
{ |memberf ((ta, tv)) tS| }
{| conf tS (!ta) -> conf tS (tv) |}

\and
\inferrule[T-ass]
{ }
{| conf tS (ta := tv) -> conf (bracket tS (mapsto ta tv)) tv |}

\and
\inferrule[T-fix]
{ }
{| conf tS (fix (\ x . e)) -> conf tS ({fix (\ x . e)/x} e) |}

\end{mathpar}

\caption{|targetLangML|: simple untyped lambda calculus extended with booleans,
mutable references and general recursion. |FV(te)| returns the set of free
variables in expression |te|.}
\label{fig:ml-full}
\end{figure}

### 2014-10-17 paper/retrofit.tex
move semantics to appendix

\begin{figure}
\begin{align*}
    & |toLabeled l te @= | \\
    & |tab let i = taskId in| \\
%%    & |tab let j = TI (sandbox (IT (TI (setLabel l); TI (send i l (IT te)))))| \\
    & |tab let j = TI (sandbox (IT (TI (send i l (IT te)))))| \\
    & |tab in (\ _ . TI (setLabel l); TI (recvf x _ x unit))|
\end{align*}
\caption{Encoding of toLabeled using isolated tasks.}\label{fig:toLabeled}
\end{figure}

When considering tasks, we will instead say that the allocation of a new
stack frame with a raised label corresponds to the creation of a new
isolated task; a sample encoding using our language is shown in
Figure~\ref{fig:toLabeled}.
There is one more ingredient: in a stack discipline, one generally
expects stack entries to be processed in order, rather than in parallel
as would be suggested by isolated tasks.  The sequential processing of
the task queue corresponds to a specific \emph{scheduling policy} of
these tasks.  In fact, the choice of scheduling here is the essential difference that
determines whether or not one can prove termination-insensitive or
termination-sensitive non-interference. We will show how different
scheduling policies give different security guarantees.

@@

\and
\inferrule[T-ifFalse]
{ } {| conf tS (if false then te1 else te2) -> conf tS te2|}

\and
\inferrule[T-ref]
{ | fresh ta | }
{| conf tS (ref tv) -> conf (bracket tS (mapsto ta tv)) ta |}

\and
\inferrule[T-deref]
{ |memberf ((ta, tv)) tS| }
{| conf tS (!ta) -> conf tS (tv) |}

\and
\inferrule[T-ass]
{ }
{| conf tS (ta := tv) -> conf (bracket tS (mapsto ta tv)) tv |}

\and
\inferrule[T-fix]
{ }
{| conf tS (fix (\ x . e)) -> conf tS ({fix (\ x . e)/x} e) |}

%\and
%\inferrule[T-fail]
%{ }
%{| conf tS ( tE [ fail ] ) -> conf tS fail |}
\end{mathpar}

\caption{|targetLangML|: simple untyped lambda calculus extended with booleans,
mutable references and general recursion. |FV(te)| returns the set of free
variables in expression |te|.}
\label{fig:ml}
\end{figure}

>>>>

When considering tasks, we will instead say that the allocation of a new
stack frame with a raised label corresponds to the creation of a new
isolated task; a sample encoding using our language is as follows:
\begin{align*}
    & |toLabeled l te @= | \\
    & |tab let i = taskId in| \\
%%    & |tab let j = TI (sandbox (IT (TI (setLabel l); TI (send i l (IT te)))))| \\
    & |tab let j = TI (sandbox (IT (TI (send i l (IT te)))))| \\
    & |tab in (\ _ . TI (setLabel l); TI (recvf x _ x unit))|
\end{align*}
There is one more ingredient: in a stack discipline, one generally
expects stack entries to be processed in order, rather than in parallel
as would be suggested by isolated tasks.  The sequential processing of
the task queue corresponds to a specific \emph{scheduling policy} of
these tasks.  In fact, the choice of scheduling here is the essential difference that
determines whether or not one can prove termination-insensitive or
termination-sensitive non-interference. We will show how different
scheduling policies give different security guarantees.

@@

\end{mathpar}

\caption{|targetLangML|: simple untyped lambda calculus extended with booleans,
mutable references and general recursion.  For space reasons we only show two
representative reduction rules;  full rules can be found in \appref{sec:app:semantics}.}
\label{fig:ml}
\end{figure}
